Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-06-11 thirdPaper/draft/typeConeAssociahedra.tex
changes biblio + poster

\medskip
To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics in particular through further developments of the amplituhedron program open in~\cite{ArkaniHamedBaiHeYan}.

>>>>

\medskip
To conclude, it is our hope that the present paper will participate to the interactions between combinatorial geometry, representation theory, and mathematical physics; in particular through further developments of the amplituhedron program, which was open in~\cite{ArkaniHamedTrnka-Amplituhedron} and has flourished during the last years~\cite{ArkaniHamedBourjailyCachazoGoncharovPostnikovTrnka-GrassmannianGeometryScatteringAmplitudes}. The kinetic associahedron from~\cite{ArkaniHamedBaiHeYan} is one of the last ``positive geometries''~\cite{ArkaniHamedBaiLam-PositiveGeometries} that has emerged in the study of scattering amplitudes.
